# Week 3 Short Answer Questions

## Noah Zwiefel

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

5.1.

``` {r}
library(mosaicData)
library(DataComputing)
ggplot(data=CPS85,aes(x=sex,y=wage ,fill=married))+geom_bar(stat='identity',position='dodge', width=.9)+ facet_wrap(~race,ncol=3) 
```

5.2.

``` {r}
HappinessIndex %>%
WorldMap(key="country",fill="corruption")
```

6.5:

b.

6.6

d.

6.7:

a.

6.8:


``` {r}
Small <-
  NCHS %>%
  sample_n(size=5000)

ggplot(data=Small,aes(x=bmi,y=weight))+geom_point()+aes(colour=smoker)
```

7.1.

a. mean()
b.  summarise(var1 = var2/var3, na.rm=TRUE)
c. order()?
d. filter()
e. filter() (also subset())
f. summarise()


7.4.

a.quotation marks around "first" are unnesc.
b.the ref to "Tmp" in summarise is unnesc, given that we're piping data in
c. missing the %>%/pipe between the commands. Won't get the expected results.

7.5.

7.7. 

7.11.

a. the total # of patients of each sex, along with the mean age 
b. the total # of patients for each diagnosis, and mean age
c. a count for each combination of sex + diagnosis, along with mean age 
d. count for patients grouped by age and diagnosis + mean age 
e. count for patients of each age group + mean age


7.12.

1. dim()
2. names()
3.help()
4.library()
5.
6.
