# Week 6 Project

## Noah Zwiefel

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

``` {r cache=TRUE}
data_site <- 
  "http://tiny.cc/dcf/2014-Q4-Trips-History-Data-Small.rds" 
Trips <- readRDS(gzcon(url(data_site)))

```

1.

``` {r}
Trips %>% ggplot(aes(x=sdate)) + geom_density()
```

More people checked out bikes in Oct and Nov vs Dec and Jan.

2.

``` {r}
Trips %>% 
  mutate(time_of_day = 
       lubridate::hour(sdate) + 
         lubridate::minute(sdate) / 60) %>%
ggplot(aes(x=time_of_day)) + geom_density()
```

Mostly checked out bikes in the am between 8-9, and pm between 4-7 or so.

3.

``` {r}
Trips %>% 
  mutate(time_of_day = 
       lubridate::hour(sdate) + 
         lubridate::minute(sdate) / 60) %>% mutate(day_of_week=lubridate::wday(sdate)) %>%
ggplot(aes(x=time_of_day)) + geom_density() + facet_wrap( ~ day_of_week)

```

4.

``` {r}
Trips %>% 
  mutate(time_of_day = 
       lubridate::hour(sdate) + 
         lubridate::minute(sdate) / 60) %>% mutate(day_of_week=lubridate::wday(sdate)) %>%
ggplot(aes(x=time_of_day,fill=client)) + geom_density() + facet_wrap( ~ day_of_week)

```

5.

``` {r}
Trips %>% 
  mutate(time_of_day = 
       lubridate::hour(sdate) + 
         lubridate::minute(sdate) / 60) %>% mutate(day_of_week=lubridate::wday(sdate)) %>%
ggplot(aes(x=time_of_day,fill=client)) + geom_density(position = position_stack()) + facet_wrap( ~ day_of_week)

```

The second one - it's easier to see what's going on.

6.

``` {R}
Trips %>% 
  mutate(time_of_day = 
       lubridate::hour(sdate) + 
         lubridate::minute(sdate) / 60) %>% mutate(wday = ifelse(lubridate::wday(sdate) %in% c(1,7), "weekend", "weekday")) %>%
    
ggplot(aes(x=time_of_day,fill=client)) + geom_density(position = position_stack()) + facet_wrap( ~ wday)

```

I'd argue that it depends on what the objective is: if the objective is to see bike usage on weekday vs weekend, it makes more sense to facet by type of day. If objective is to see casual vs client usage: it makes more sense to facet it by who uses them.