# Week 5 Project

## Noah Zwiefel

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->



Let's begin by loading stock mkt data:

``` {r}
companies <- c("VZ", "S", "T")
Prices <- 
  read_stock_prices(companies, what="daily",
                  start_year=2000, end_year=2015) 
```

1. Buy/sell profit:

Let's create a new table that gives the dates and what actions were performed. 

``` {r}
actionBuy=c("buy")
dateBuy=c("2006-01-03")
ActionsBuy = data.frame(actionBuy,dateBuy)
actionSell=c("sell")
dateSell = c("2014-12-30")
ActionsSell = data.frame(actionSell,dateSell)

```

Let's combine the tables:

``` {r}
Prices$date = as.Date(Prices$date)
ActionsBuy$date = as.Date(ActionsBuy$date)
ActionsSell$date = as.Date(ActionsSell$date)
Prices_buy <- Prices %>% inner_join(ActionsBuy,by=c(date="date"))
Prices_sell <- Prices %>% inner_join(ActionsSell,by=c(date="date"))
Prices_merged <- Prices_sell %>% inner_join(Prices_buy,by=c(company="company"))
```

next let's find the profit that was made:

``` {r}
profits <- Prices_merged %>% mutate(profit=close.x-close.y,percent=(close.x-close.y)/(close.x)) %>% select(company,profit,percent)
head(profits)
```

Indexing prices

```{r}
ref_date <- ymd("2005-01-03")
Reference <-
  Prices %>% 
  filter(date==ref_date) %>%
  select(company, standard=close)
standardized <- Prices %>% inner_join(Reference,by=c(company="company"))
standardized <- standardized %>% mutate(indexed=(close/standard))
ggplot(data=standardized,aes(x=date,y=indexed,colour=company)) + geom_line()
```

Dividends:

``` {R}
Dividends <-  read_stock_prices(companies, what="dividends") %>% filter(as.Date(date) <= ActionsSell$date & as.Date(date) >= ActionsBuy$date)
DividendsAndStocks <- Dividends %>% inner_join(Prices,by=c(company="company",date="date")) %>% mutate(div_that_they_want=dividends*close)
head(DividendsAndStocks)
#I think there's the typo in the instructions, because there's no way that they paid a dividend of $27 a share...I'm just going to disregard and move onto the next step independently
DividendEarnings <- DividendsAndStocks %>% group_by(company) %>% summarise(total_dividend=sum(dividends))
head(DividendEarnings)
head(profits)
```

Looks like in most cases, earned more from holding stock, even if only marginally more - with the exception, of course, of Sprint, where you actually had net loses, even if dividend was positive.