# Week 6 Short Answer Questions

## Noah Zwiefel

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

12.1

BabyNames %>%
  group_by(name) %>%
  summarise(total=sum(count)) %>%
  filter(rank(desc(total))<=5)

12.2

BabyNamesChg <- BabyNames %>%
  group_by(year, name) %>%
  summarise(total=sum(count)) %>%
  filter(rank(desc(total))<=100) %>%
  mutate(top_100 = TRUE)
  
BabyNamesChgOther <- BabyNames %>%
  group_by(year, name) %>%
  summarise(total=sum(count)) %>%
  filter(rank(desc(total))>100) %>%
  mutate(top_100 = FALSE)
  
BabyNameThing <- rbind(BabyNamesChg,BabyNamesChgOther)

BabyNameThing2 <- BabyNameThing %>%
  group_by(year, top_100) %>%
  summarise(total_cases=sum(total))
  
GlyphReady <- BabyNameThing2 %>%
  spread(top_100, total_cases) %>%
  mutate(top_100 = 'TRUE' / ('TRUE' + 'FALSE'))

GlyphReady %>% ggplot(aes(x=year,y=top_100)) + geom_point() + geom_smooth()

12.3

a. transformation
b. transformation
c. summary
d. other fucntion
e.other function
f. summary + transformation function
g. neither
h. summary(?)

13.1

1. 18 verticies
2. 9 edges

13.2

1. 4 verticies: A, B, C, D; A->C, A->b, C->D
2. table 2
3. table 1: shows B being connected to C (it's not...); table 3 doesn't even make sense...there's one with 3 items...

13.3

table 2



13.4

1. exports
2. population

14.1,

``` {r}
ggplot(data=mosaicData::CPS85,aes(x=sex,y=wage,color=sex)) + geom_boxplot()
```
14.3

Women have heights (mostly) between 1.5-1.7; men have heights mostly between 1.6-1.9 or so.

14.7,

``` {R}
ggplot(data=mosaicData::CPS85,aes(x=educ,y=wage,color=sex)) + geom_point(aes(alpha=.1)) + geom_smooth(method='lm')
```

14.10

``` {r}
ggplot(data=mosaicData::Galton,aes(x=height,color=sex)) + geom_density()
```