# Week 7 Short Answer Questions

## Noah Zwiefel

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

15.1

- lubridate::ymd("1997-05-02") - lubridate::mdy("April 30, 1777")
- lubridate::ymd("1997-05-02") - lubridate::mdy("06-23-1912")
- lubridate::ymd("1997-05-02") - lubridate::dmy("3 March 1847")
- lubridate::ymd("1997-05-02") - lubridate::mdy("Nov. 11th, 1918")
- lubridate::ymd("1997-05-02") - lubridate::mdy("July 20, 1969")

15.2

a. as.numeric: no; tidyr function? yes.
b. as.numeric: no; tidyr function? yes.
c. as.numeric: no; tidyr function? no.
d. as.numeric: no; tidyr function? yes.
e. as.numeric: no; tidyr function? yes.
f. as.numeric: no; tidyr function? yes.
g. as.numeric: no; tidyr function? yes.
h. as.numeric: yes; tidyr function? yes.
i. as.numeric: no; tidyr function? yes.

16.1:

``` {R}
BabyNames %>%
  filter(grepl("[aeiou]$",name)) %>%
  group_by(name) %>%
  summarise(total=sum(count)) %>%
  arrange(desc(total))
```

``` {r}
BabyNames %>%
  filter(grepl("(joe|jo)$",name)) %>%
  group_by(name) %>%
  summarise(total=sum(count)) %>%
  arrange(desc(total))
```

16.2

Looks like it matches a phone numbers that start with an area code with first digit between 2-9. All digits are being extracted.

16.3

1. 2 letters long
2. A lot of strings! There are 19 initial letters that the string can have. I'm not going to count out how many different letter possibilities could match, because I feel as if that would be a waste of time and busy work.
3. Possibly state/US territory codes.