# Week 3 Project

## Noah Zwiefel

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

``` {r}

ggplot(data = CPS85, aes(x = exper, y = wage, color = married)) + geom_point() + facet_wrap( ~ sector)

ggplot(data = NCHS, aes(x = bmi)) + geom_density(aes(color = sex,fill=TRUE)) + facet_wrap(~ pregnant)
```

## Diamonds

1. 
Which color diamonds seem to be largest on average (in terms of carats)?



``` {r}
diamonds %>% 
  group_by(color) %>% 
  summarise(avg_carat_size=mean(carat)) %>% 
  arrange(desc(avg_carat_size)) %>% 
  head( 1 )
```

2. 
Which clarity of diamonds has the largest average “table” per carat?

``` {r}
diamonds %>% 
  group_by(clarity) %>% 
  summarise(avg_table_size=mean(table)) %>% 
  arrange(desc(avg_table_size)) %>% 
  head( 1 )
```

## Vote

1. 

How many cases are there?


``` {r}
dim(Minneapolis2013)
```

2. 
Who were the top 5 candidates in the Second vote selections.

``` {r}
Minneapolis2013 %>% 
  group_by(Second) %>% 
  tally() %>% 
  arrange(desc(n)) %>%
  head()
```

3.

How many ballots are marked “undervote” in
- First choice selections?
- Second choice selections?
- Third choice selections?

``` {r}
Minneapolis2013 %>%
  subset(First == "undervote") %>%
  tally()
Minneapolis2013 %>%
  subset(Second == "undervote") %>%
  tally()
Minneapolis2013 %>%
  subset(Third == "undervote") %>%
  tally()

```

4.

``` {r}
Minneapolis2013 %>%
  subset(First=="BETSY HODGES") %>%
  group_by(Second) %>% 
  tally() %>% 
  arrange(desc(n)) %>%
  head()
```

Looks like it's Mark Andrew.

5.

``` {r}
Minneapolis2013 %>%
  group_by(Precinct) %>%
  summarise(percentage=base::mean(First=="undervote")) %>%
  arrange(desc(percentage)) %>%
  head()
```

looks like P-6C has the highest % of precincts that had first=="undervote"